---
title: "p8105_hw3_as5685"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(p8105.datasets)
```

## load in "instatcart" dataset
```{r}
data("instacart")
```

## number of aisles and items ordered
```{r}
aisles_data = 
instacart %>% 
  group_by(aisle) %>% 
  summarize(
    aisle_number = n()
  ) %>% 
  filter(min_rank(desc(aisle_number)) < 2) %>% 
  knitr::kable()
```
The number of aisles are 134. 
Fresh vegatables is the  most item ordered from. 

## plot for number of items ordered
```{r}
popularitem_plot = 
    instacart %>% 
      group_by(aisle) %>% 
      summarize(
      n = n()
      ) %>% 
    filter(n > 10000) %>% 
    ggplot(aes(y = aisle, x = n)) +
      geom_point()
```

## table showing three most popular items
```{r}
popularitem_data =
  instacart %>% 
   group_by(aisle, product_name) %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  summarize(
    product_order_number = n()
  ) %>% 
  filter(min_rank(desc(product_order_number)) < 4) %>% 
  knitr::kable()
```

## mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week
```{r}
meanhours_data = 
instacart %>% 
  group_by(product_name,order_dow) %>% 
    filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  summarize(meanhours = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = "order_dow",
    values_from = "meanhours"
  ) %>% 
knitr::kable(digits = 1) 
```

## Problem 2 
## load and read in data "BRFSS"
```{r}
data("brfss_smart2010")
```

## data cleaning 
```{r}
brfss_dataclean = 
  brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  filter(response %in% c("Excellent","Fair","Good","Poor","Very good")) %>% 
  mutate(
    response = factor(response, levels = c("Poor","Fair","Good","Very good","Excellent")) 
    ) 
```

## states obseved at 7 or more.
```{r}
location_count_2002 = 
brfss_dataclean %>% 
   filter(year %in% c("2002","2010")) %>% 
    group_by(year, locationabbr) %>%
    summarize(
      state_n = n(),
      location_n = n_distinct(locationdesc)
    ) %>% 
  mutate(greatherthan7 = location_n >= 7) %>% 
  filter(greatherthan7 == "TRUE")
```
In 2002, "NJ", "PA","NC", "MA", "FL","CT" is the state obeserved at 7 locations. In 2010, "CA","FL","CO","MA","MD","NC","NE","NJ","NY","OH","PA", "SC","TX","WA" are the states observed at 7 or more locations. 


## spaghetti plot
```{r}
excellent_datasets = 
  brfss_dataclean %>%
  group_by(locationabbr,year) %>% 
  filter(response == "Excellent") %>% 
  mutate(
    datavalue_mean = mean(data_value, na.rm = TRUE)
  ) %>% 
  select(year, locationabbr, datavalue_mean,response) %>% 
  distinct()

spaghetti_plot = 
  ggplot(data = excellent_datasets, aes(x = year, y = datavalue_mean, color = locationabbr)) +
  geom_line()
```

## two-panel plot
```{r}
plot = 
  brfss_dataclean %>% 
  filter(year %in% c("2006","2010"), locationabbr == "NY") %>% 
  select(response,year,locationdesc,data_value) %>% 
  ggplot(aes(x = data_value, fill = response)) + 
    geom_density() +
    facet_grid(.~locationdesc) 
    #viridis::scale_fill_viridis(discrete = TRUE)
```
## problem 3

## load, tidy and wrangle the data
```{r}
CHF_data = 
  read_csv("./p8105_hw3_as5685_files/accel_data.csv") %>% 
  janitor::clean_names() %>% 
  
  mutate(
    day = factor(day, levels = c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday", "Sunday")),
    weekday = day %in% c("Monday","Tuesday","Wednesday","Thursday","Friday") 
    ) %>% 
    
    select(week,day_id,day,weekday,everything()) %>% 
      
  pivot_longer(
    activity_1:activity_1440, 
    names_to = "activity_num",
    values_to = "count_for_minute")
```
I used `pivot_longer` to organize the table. The variables are `week`, `day_id`, `day`, `weekday`, `activity number` and `count_for_minute`

## aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals.
```{r}
totalactivity_data = 
  CHF_data %>% 
  group_by(day_id) %>% 
  mutate(
   day_total_activity = sum(count_for_minute)
  ) %>% 
  select(day_id,day_total_activity) %>% 
  distinct()
  knitr::kable
```

## single-panel plot
```{r}
activity_plot = 
  CHF_data %>% 
  ggplot(aes(x = week, y = count_for_minute, color = day)) +
  geom_point() 
```










